Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-07 doc/report/msc-report.tex
moved intro to abstract, added TODO thoughts to intro plus cosmetic changes.

\begin{document}

\maketitle

\noindent \Large{\textbf{Abstract}}

\vspace{12pt}

\noindent This is where we put down two to four sentences about:
Introduction, problem, existing tools, our solution and implementation,
conclusions.

\tableofcontents

\vfill

@@

This thesis talks about a data store for aggregated multi-dimensional time-series-based data. The data is aggregated over many units of measurements and across multiple dimensions. One of these dimensions is always time.

Zohmg solves the problem of summing and storing measurements taken from log files or similar. It stores solely summarized data, not atomic data. Zohmg is optimized for speed of data retrieval.

The thesis is presented in three major sections: problem statement, the theoretical solution and the implementation details.

Says Wikipedia: "Data warehouse is a repository of an organization's electronically stored data. Data warehouses are designed to facilitate reporting and analysis." The main actions of a data warehouse is extract, transform and load data, although not necessarily in that order.

@@

It is assumed that the audience of this paper has at least a basic
understanding of how one models data in relational databases. As will
quickly become apparent, a BigTable-like \cite{bigtable} data store is
drastically different from the relational model, meaning that those who
know their table schemas will have some un-learning to do before being able
to fully grasp the leaner BigTable-model.

% TODO: necessity of this paragraph?
The reader is also assumed to possess basic understanding about distributed
systems, with focus on high level abstractions rather than detailed
knowledge about practical implementation details.

@@

This thesis, fully, describes the Zohmg system and how to use it.

Chapter 2 the theoretical base of the problem statement is established.

In chapter 3 the tools used for the implementation are declared, moving
over to chapter 4 where the details of the implementation are presented.

@@

A data cube is a conceptual n-dimensional array of values. The values are
numerical facts belonging to some dimension. The data cube is also known as a
hypercube, it relates to multidimensional analogues of squares and cubes.
In this context, each dimension of the cube corresponds to an attribute of
the data in question and each point along the dimension's axis is a value of
the corresponding attribute. The mental model of a data cube aids in
reasoning about dimensions. Data cubes are traditionally modeled as star
schemas in relational database systems. \cite{olap_solutions}

@@

We have built a system---henceforth called Zohmg---which has the goal of being
a large scale aggregating data warehouse for time-series-based log-like
data sources.

>>>>

\begin{document}
\maketitle

\noindent \Large{\textbf{Abstract}}
\vspace{12pt}

\noindent 
This thesis describes a data store for multi-dimensional time-series-based data. The data is aggregated over many units of measurements and across multiple dimensions. One of these dimensions is always time.

Zohmg solves the problem of summing, storing and serving measurements. These measurements may be taken from log files or similar sources. Zohmg stores only the summarized data, not the atomic measurements. Zohmg is optimized for speed of data retrieval.

The thesis is presented in three major sections: problem statement, theoretical solution and implementation details.

\tableofcontents
\vfill
\pagebreak

@@

% TODO: den har texten passar battre i ett eget stycke/sektion, background reading style.
Says Wikipedia: "Data warehouse is a repository of an organization's electronically stored data. Data warehouses are designed to facilitate reporting and analysis." The main actions of a data warehouse is extract, transform and load data, although not necessarily in that order.

@@

@@

This thesis describes the Zohmg system and how to use it.

In chapter 2, the theoretical base of the problem statement is established.

In chapter 3, the tools used for the implementation are declared, moving
over to chapter 4 where the details of the implementation are presented.

@@

A data cube is a conceptual n-dimensional array of values. The values are
numerical facts belonging to some dimension. The data cube is also known as a
hypercube. The data cube relates to multidimensional analogues of squares and cubes.
In this context, each dimension of the cube corresponds to an attribute of
the data in question and each point along the dimension's axis is a value of
the corresponding attribute. The mental model of a data cube aids in
reasoning about dimensions. Data cubes are traditionally modeled as star
schemas in relational database systems. \cite{olap_solutions}

@@

We have built a system---henceforth called Zohmg---which has the goal of being
a large scale aggregating data store for time-series-based log-like
data sources.
